% --- LaTeX CV Template - Luyu Liu ---

% Set document class and font size
\documentclass[letterpaper, 11pt]{article}
\usepackage[utf8]{inputenc}

% Package imports
\usepackage{setspace, longtable, graphicx, hyphenat, hyperref, fancyhdr, ifthen, everypage, enumitem, amsmath, setspace}

% --- Page layout settings ---

% Set page margins
\usepackage[left=1in, right=1in, bottom=0.7in, top=0.7in]{geometry}

% Set line spacing
\renewcommand{\baselinestretch}{1.15}

% --- Page formatting ---

% Set link colors
\usepackage[dvipsnames]{xcolor}
\hypersetup{colorlinks=true, linkcolor=RoyalBlue, urlcolor=RoyalBlue}

% Set font to Libertine, including math support
\usepackage{libertine}
\usepackage[libertine]{newtxmath}
% Remove page numbering
\pagenumbering{gobble}

% --- Document starts here ---

\begin{document}

% Name and date of last update to this document
\noindent{\Huge{Luyu Liu}
\hfill{\it\large} \\
\null \hfill{\it\large } \\
}
\hfill{  The Ohio State University} \hfill{\large \textbf{Email}: \href{liu.6544@osu.edu}{liu.6544@osu.edu}} \\
\hfill{Department of Geography} \hfill{\large \textbf{Website}: \href{https://luyuliu.github.io}{https://luyuliu.github.io}} \\
\hfill{0126 Derby Hall} \hfill{\large \textbf{GitHub}: \href{https://github.com/luyuliu}{https://github.com/luyuliu}} \\
{154 North Oval Mall} \\
{Columbus, OH 43210-1361} \\

% --- Start the two-column table storing the main content ---

% Set spacing between columns
\setlength{\tabcolsep}{0pt}

% Set the width of each column
\begin{longtable}{p{6.5in}}
% --- Section: Research interests ---

\nohyphens{\textbf{Research interests}} \\
Accessibility, Public transit, Micro-mobility, Mobility equity \\
\\

% --- Section: Education ---

\textbf{Education} 
\\ The Ohio State University, Department of Geography \hfill Columbus, Ohio \\
Ph.D. Geography \hfill Aug 2019 -- Present \\

\\ The Ohio State University, Department of Educational Studies \hfill Columbus, Ohio \\
Graduate Certificate in College and University Teaching \hfill Aug 2020 -- Aug 2021 \\

\\ The Ohio State University, Department of Geography \hfill Columbus, Ohio \\
M.A. Geography \hfill Aug 2017 -- Jul 2019 \\

\\ Peking University, College of Urban and Environmental Sciences \hfill Beijing, China \\
B.S. Environmental Science \hfill Sep 2013 -- Jul 2017 \\

\\ Peking University, School of Mathematical Sciences \hfill Beijing, China \\
B.S. Mathematics and Applied Mathematics \hfill Sep 2014 -- Jul 2017 \\ \\

% --- Uncomment the next few lines if you want to include some courses ---
%& \textbf{Selected coursework}
%\begin{itemize}[noitemsep,leftmargin=*]
%\item \underline{Relevant subject 1}: Course 1, Course 2, Course 3, Course 4
%\item \underline{Relevant subject 2}: Course 1, Course 2, Course 3, Course 4
%\end{itemize} \\

% --- Section: Awards, scholarships, etc. ---
% --- Note: section title is spread over two lines ---

{\textbf{Thesis}}\\

Accessibility in Motion: Measuring Real-time Accessibility with Dynamic Data \hfill Aug 2019 -- present \\ 
\begin{tabular}{p{5in}}
Ph.D. dissertation, The Ohio State University, with Dr. Harvey Miller, Dr. Ningchuan Xiao, Dr. Huyen Le, and Dr. Andre Carrel
\end{tabular} \\ \\

\begin{tabular}{p{5in}}
Public transit transfer risk with high-resolution schedule and real-time bus data 
\end{tabular} \hfill Feb 2018 -- Aug 2019 \\
\begin{tabular}{p{5in}}
Master's thesis, The Ohio State University, with Dr. Harvey Miller, Dr. Ningchuan Xiao, and Dr. Morton O'Kelly
\end{tabular} \\ \\


Measuring and Decomposing Global CO2 emission Inequality \hfill Feb 2015 -- Jun 2017 \\ 
\begin{tabular}{p{5in}}
Undergraduate thesis, Peking University, with Dr. Bengang Li
\end{tabular} \\ \\

% --- Section: Publications ---
\nohyphens{\textbf{Publications}} \\
\underline{Journal Articles} \\
\textbf{Liu, L.}, \& Miller, H. J. (2020). Measuring risk of missing transfers in public transit systems using high-resolution schedule and real-time bus location data. Urban Studies, 0042098020919323.\\\\

\textbf{Liu, L.}, \&  Miller, H. J. (2020). Does real-time transit information reduce waiting time? An empirical analysis. Transportation Research Part A: Policy and Practice, 141, 167-179.\\\\

\textbf{Liu, L.}, Miller, H. J., \& Scheff, J. (2020). The impacts of COVID-19 pandemic on public transit demand in the United States. Plos one, 15(11), e0242476.\\\\

Park, Y., Mount, J., \textbf{Liu, L.}, Xiao, N., \& Miller, H. J. (2019). Assessing public transit performance using real-time data: spatiotemporal patterns of bus operation delays in Columbus, Ohio, USA. International Journal of Geographical Information Science, 1-26.\\\\

\underline{Conference and Presentation} \\
\textbf{Liu, L.}, Miller, H. J. (2021). Revisiting the Impacts of Transit Real-time Information on Waiting Time Reduction: An Empirical Analysis in Columbus, Ohio. At American Association of Geographers Annual Meeting 2021.	\\\\

\textbf{Liu, L.}, Miller, H. J. (2019). Measuring public transit transfer risk using highresolution schedule and real-time location data. At American Association of Geographers Annual Meeting 2019, Washington, DC. \\\\

Root, E. D., \textbf{Liu, L.}, Porr, A. (2019). Addressing birth outcomes with data analytics and spatial analysis. At 18th International Medical Geography Symposium 2019, Queenstown, New Zealand.	\\\\

% --- Section: Research experience ---

\nohyphens{\textbf{Research Project Experience}} \\
MORPC Sustainability Dashboard \hfill Mar 2019 -- Sep 2020 \\
The Ohio State University, with Dr. Harvey Miller and Dr. Ningchuan Xiao \\
Visualize sustainability progress in a holistic dashboard with integrated backend. \\\\

Columbus Urban \& Regional Information Observatory (CURIO) \hfill Aug 2017 -- Oct 2018 \\
The Ohio State University, with Dr. Harvey Miller and Dr. Ningchuan Xiao \\
Visualize the geographic information in city of Columbus in comprehensive web-map \\\\

Infant Mortality Research Partnership (IMRP) Online GIS Platform \hfill May 2018 -- Aug 2019 \\
The Ohio State University, with Dr. Elisabeth Root \\
Integrate and visualize public health and GIS data in a holistic web-based platform \\\\

Neighborhood Polygon Algorithm Based on Network Analysis \hfill Nov 2017 -- May 2018 \\
The Ohio State University, with Dr. Christopher Browning, Dr. Catherine Calder \\
Develop algorithm generating neighborhood polygons based on road network \\\\

% --- Section: Teaching experience ---

\textbf{Teaching and Public Speaking} \\
Ohio State University GEOG 5210: Fundamental GIS, 3 credits \hfill May 2021 -- July 2021 \\
Instructor, student SEI rating: 4.71/5 (University average: 4.48), 34 enrollments \\\\

UCGIS Workshop: Full-stack Geo-visualization 101: How to Make Productive Webmaps \hfill June 2021 \\
Instructor, participants rating: 4.44/5, 19 enrollments \\\\

Harvard University Vizathon: Learn to Make Your First Web Map \hfill July 2021\\
Workshop organizer and instructor \\\\

Ohio State University GEOG 2200: Mapping Our World \hfill Feb 2020\\
Guest lecturer on geo-visualization \\\\

West Washington University ENVS 412: Environmental Journalism \hfill Jan 2021\\
Guest lecture on COVID impact on public transit \\\\

\begin{tabular}{p{5in}}
Ohio State News: "Pandemic has surprising impacts on public transit demand" from https://news.osu.edu/pandemic-has-surprising-impacts-on-public-transit-demand/
\end{tabular} \hfill Nov 2020 \\\\

\begin{tabular}{p{5in}}
Ohio State News: "Want to wait less at the bus stop? Beware real-time updates" from https://news.osu.edu/want-to-wait-less-at-the-bus-stop-beware-real-time-updates/ 
\end{tabular} \hfill Oct 2020 \\\\

% --- Section: Grant ---
\textbf{Grant} \\
"Sharpe Innovation Commons Seed Grant Award" by Geography OSU - \$5000 \hfill 2020 \\
"Everest Project" by Department of Education and Peking University - \$6000 \hfill 2014 -- 2017 \\\\

% --- Section: Award ---
\textbf{Award} \\
TR Lakshmanan and Lata Chatterjee Awards 2020 \hfill 2020 \\
\begin{tabular}{p{5in}}
Collaborative Achievement in Sustainability Award from Mid-Ohio Regional Planning Commission (as group) \end{tabular}\hfill 2020 \\
Scholarship of Tiehan, PKU, 2013-2016 \hfill 2013 -- 2016 \\
Honorable Mentioned by “Mathematical Contest in Modeling” Sponsored by COMAP \hfill 2016 \\
President of "Outstanding Class" award winner of PKU in 2015 \hfill 2015 \\\\

% --- Section: Service ---
\textbf{Service}\\
\underline{Peer Review for Journals}\\
Sustainable Cities and Society \\
Journal of Transport Geography \\
Journal of Geographical Systems \\
Public Transport \\
Transportation \\
International Journal of Geo-Information \\
Transportation Research Part C: Emerging Technologies \\ 
Journal of Public Transportation \\ 
American Journal of Infection Control \\\\


\underline{Department/University Service}\\
Graduate Geography Organization, Social Chair \hfill Sep 2021 -- Present\\

% --- End of CV! ---

\end{longtable}
\end{document}

